\documentclass[11pt]{article}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.5in, right=0.5in]{geometry}

\usepackage[utf8]{inputenc}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{titlesec}
\raggedright
\pagestyle{empty}
\input{glyphtounicode}
\pdfgentounicode=1

\titleformat{\section}{\bfseries\large}{}{0pt}{}[\vspace{1pt}\titlerule\vspace{-6.5pt}]
\renewcommand\labelitemi{$\vcenter{\hbox{\small$\bullet$}}$}
\setlist[itemize]{itemsep=-2pt, leftmargin=12pt, topsep=7pt}

\begin{document}

\centerline{\Huge John Doe}
\vspace{5pt}
\centerline{\href{mailto:name@gmail.com}{name@gmail.com} | \href{https://mitcommlab.mit.edu/meche/commkit/portfolio/}{portfolio.com} | \href{https://old.reddit.com/r/EngineeringResumes/wiki/index\#wiki_portfolios}{github.com/name}}
\vspace{-10pt}

\section*{Summary}
Highly skilled software engineer with expertise in Python, AWS, and Terraform. Proven ability to build robust APIs using FastAPI.

\section*{Core Skills}
Python, AWS, Terraform, FastAPI, RESTful APIs, Docker, Kubernetes, CI/CD, Agile methodologies

\section*{Achievements}
\begin{itemize}
    \item \textbf{Built API:} Built a scalable and secure API using FastAPI, resulting in improved system performance and user experience. \href{https://fastapi.tiangolo.com/}{FastAPI documentation}
    \item \textbf{Optimized AWS Costs:} Implemented Terraform for infrastructure management, reducing AWS costs by 30\%. \href{https://aws.amazon.com/terraform/}{Terraform on AWS}
    \item \textbf{Streamlined CI/CD:} Introduced Docker and Kubernetes for containerization and orchestration, accelerating deployment cycles by 40\%. \href{https://kubernetes.io/}{Kubernetes}
    \item \textbf{Enhanced Collaboration:} Facilitated Agile methodologies, improving team collaboration and project delivery. \href{https://www.mountaingoatsoftware.com/agile/scrum}{Agile methodologies}
    \item \textbf{Improved System Resilience:} Implemented monitoring and logging solutions, enhancing system resilience and reducing downtime. \href{https://aws.amazon.com/cloudwatch/}{AWS CloudWatch}
\end{itemize}

\section*{Projects}
\textbf{API Project} \hfill \href{https://github.com/name/api-project}{github.com/name/api-project}
\begin{itemize}
    \item Developed a RESTful API using FastAPI, Docker, and Kubernetes for seamless deployment and scalability.
    \item Implemented Terraform for infrastructure management, reducing AWS costs by 30\%.
\end{itemize}

\textbf{CI/CD Project} \hfill \href{https://github.com/name/ci-cd-project}{github.com/name/ci-cd-project}
\begin{itemize}
    \item Designed and implemented a CI/CD pipeline using Docker and Kubernetes, accelerating deployment cycles by 40\%.
    \item Integrated monitoring and logging solutions to enhance system resilience and reduce downtime.
\end{itemize}

\section*{Education}
\textbf{School} -- PhD in Computer Science \hfill June 2010
\textbf{School} -- MS in Computer Science \hfill June 2006
\textbf{School} -- BS in Computer Science \hfill Apr 2004

\section*{Certifications}
\textbf{Certification Name} -- Issuer \hfill Date
\href{https://certificate-link.com}{Certificate Link}

\end{document}

This LaTeX document follows the specified structure and includes a summary, core skills, achievements, projects, education, and certifications sections. The content is tailored to reflect the provided job description and candidate skills. The document should compile without errors or conflicts.